SMT-Boosted Security Types for Low-Level MPC

### 2025-11-05 toplas26/sty.tex
checkpoint

$$
\begin{array}{rclr}
  \sty &::=& \sharety \mid \pubty \mid \outty & \textit{share types} \\
  \stt &::=& [\phi,\phi] \mid \pubx{\phi} & \textit{share terms} 
\end{array}
$$

@@

\begin{mathpar}
  \inferrule[Share]
      {\eqs \models \mx{z}{\cid_2} \eop \phi - \rx{y}{\cid_1} \\ \cid_1 \ne \cid_2}
      {\eqs \vdash \Gamma,R \stredx \Gamma \cup \setit{[\mx{z}{\cid_2}, \rx{y}{\cid_1}] : \sharety}, R \uplus \setit{\rx{y}{\cid_1}}}

  \inferrule[SecOpen]
      {
        \Gamma, \eqs \vdash [\px{x},\px{y}] : \sharety\\
        \eqs \models  \px{x} + \px{y} \eop \phi' - \rx{y}{\oid}
      }
      {\eqs \vdash \Gamma,R \stredx \Gamma \cup \setit{\pubx{\px{x} + \px{y}}  : \pubty}, R \uplus \setit{\rx{y}{\cid_o}}}

  \inferrule[Reveal]
      {
        \Gamma, \eqs \vdash [\px{x},\px{y}] : \sharety
      }
      {\eqs \vdash \Gamma,R \stredx \Gamma \cup \setit{\pubx{\px{x} + \px{y}}  : \outty}, R}

  \inferrule[Output]
      {
        \Gamma, \eqs \vdash \pubx{\out{\cid}} : \outty
      }
      {\eqs \vdash \Gamma,R \stredx \Gamma \uplus \setit{\pubx{\out{\cid}} : \outty}, R}
\end{mathpar}

>>>>

$$
\begin{array}{rcl@{\hspace{10mm}}l}
  \sty &::=& \sharety \mid \pubty \mid \outty & \textit{share types} \\
  \stt &::=& [\phi,\phi] \mid \pubx{\phi} & \textit{share terms} 
\end{array}
$$

\subsection{Non-interactive typing rules}

@@

\subsection{Interactive typing rules}

\styinteractivefig

\subsection{Share Type Soundness}

\begin{definition}
  We write $\eqs,\Gamma,R : {OK}$ iff both of the following conditions hold:
  \begin{enumerate}[\hspace{5mm}i.]
  \item For all $([\mx{z}{\cid}, \rx{y}{\cid'}] : \sharety) \in \Gamma$,
    we have $\eqs \models \mx{z}{\cid} \eop \phi - \rx{x}{\cid'}$ for
    some $\phi$ and unique $\rx{x}{\cid'} \in R$, with $\cid \ne \cid'$.
  \item For all $([\phi] : \pubty) \in \Gamma$,
    we have $\eqs \models \phi \eop \phi' - \rx{x}{\oid}$ for
    some $\phi'$ and unique $\rx{x}{\oid} \in R$.
  \end{enumerate}
\end{definition}

\begin{lemma}
  Given $\eqs,\Gamma,R  : {OK}$.
  and $\eqs  \vdash \Gamma,R \stredx R',\Gamma'$.
  Then $\eqs, \Gamma',R' : {OK}$.
\end{lemma}

\begin{definition} Define $\ov(\Gamma)$ as follows:
\begin{eqnarray*}
\ov(\varnothing) &=& \varnothing \\[-1.5mm]
\ov(\setit{[\mx{z}{\cid}, \rx{y}{\cid'}] : \sharety} \cup \Gamma) &=& \setit{\mx{z}{\cid}} \cup \ov(\Gamma)\\[-1.5mm]
\ov(\setit{[\phi + \px{x}] : \pubty} \cup \Gamma) &=& \setit{\px{x}} \cup \ov(\Gamma)\\[-1.5mm]
\ov(\setit{[\phi] : \outty} \cup \Gamma) &=& \setit{\phi} \cup \ov(\Gamma)
\end{eqnarray*}
\end{definition}

\begin{lemma}
  Assume given $\Gamma,R, \eqspre \wedge \toeq{\prog} : {OK}_\cid$  and
  $\iov(\prog) = S \cup V \cup O$
  and $\Gamma, \eqspre \wedge \toeq{\prog} \vdash [\phi_1,\phi_2] : \sharety$.
  Then, letting $X \defeq \ov(\Gamma) \cap \realviews{\setit{\cid_1}}{\setit{\cid_2}}$:
  $$
  \condd{\progtt(\prog)}{S_{\setit{\cid_1}}}{S_{\setit{\cid_2}}  \cup X \cup \setit{\phi_1 + \phi_2}}
  = 
  \condd{\progtt(\prog)}{S_{\setit{\cid_1}}}{S_{\setit{\cid_2}} \cup X \cup \setit{\phi_1 + \phi_2, \phi_1}}
  $$
\end{lemma}

\begin{lemma}
  Assume given $\eqspre \wedge \toeq{\prog}, \Gamma,R: {OK}_\cid$  and
  $\iov(\prog) = S \cup V \cup O$
  and $\Gamma, \eqspre \wedge \toeq{\prog} \vdash [\phi_1,\phi_2] : \sharety$.
  Then, letting $X \defeq \ov(\Gamma) \cap \realviews{\setit{\cid_1}}{\setit{\cid_2}}$ for
  $\cid_1 \ne \cid_2$:
  $$
  \condd{\progtt(\prog)}{S_{\setit{\cid_1}}}{S_{\setit{\cid_2}}  \cup X \cup \setit{\phi_1 + \phi_2}}
  = 
  \condd{\progtt(\prog)}{S_{\setit{\cid_1}}}{S_{\setit{\cid_2}} \cup X \cup \setit{\phi_1 + \phi_2, \phi_1}}
  $$
\end{lemma}

\begin{lemma}
  Assume given $\eqspre \wedge \toeq{\prog}, \Gamma_1,R_1: {OK}_\cid$  and
  $\iov(\prog) = S \cup V \cup O$
  and $\eqspre \wedge \toeq{\prog} \vdash \Gamma_1,R_1 \stredx \Gamma_2,R_2$.
  Letting $X_1 \defeq \ov(\Gamma_1) \cap \realviews{\setit{\cid_1}}{\setit{\cid_2}}$,
  for $\cid_1 \ne \cid_2$ assume also:
  $$
  \condd{\progtt(\prog)}{S_{\setit{\cid_1}}}{S_{\setit{\cid_2}}  \cup X_1 \cup O}
  = 
  \condd{\progtt(\prog)}{S_{\setit{\cid_1}}}{S_{\setit{\cid_2}} \cup O}
  $$
  Then, letting $X_2 \defeq \ov(\Gamma_2) \cap \realviews{\setit{\cid_1}}{\setit{\cid_2}}$,
  we have:
  $$
  \condd{\progtt(\prog)}{S_{\setit{\cid_1}}}{S_{\setit{\cid_2}}  \cup X_2 \cup O}
  = 
  \condd{\progtt(\prog)}{S_{\setit{\cid_1}}}{S_{\setit{\cid_2}} \cup O}
  $$
\end{lemma}

\begin{theorem}[Share Type Soundness]
  Assume given $\prog$ with 
  $\iov(\prog) = S \cup V \cup O$
  and $\eqspre \wedge \toeq{\prog} \vdash \varnothing,\varnothing \stredx^*
  \Gamma,R$ where $\realviews{\setit{\cid_1}}{\setit{\cid_2}} \cup O
  \subseteq \ov(\Gamma)$ for all $\cid_1$, $\cid_2$ with $\cid_1 \ne \cid_2$.
  Then $\prog$ satisfies noninterference modulo output.
\end{theorem}
